---
graphics: yes
name: Milena
surname: Vásquez-Amézquita
position: "Associate Professor"
address: "Faculty of Psychology, Universidad El Bosque"
phone: (+57) 601-6489000 Ext. 1605
email: "mvasquezam@unbosque.edu.co"
www: grupo-codec.netlify.app/author/milena-vasquez-amezquita/
orcid: 0000-0001-7317-8430
googlescholar: XgNEpfgAAAAJ
researchgate: Milena-Vasquez-Amezquita
profilepic: "../images/MVA.jpg"
aboutme: |
  I am a researcher primarily interested in the neurocognitive bases of human affect and sexuality.
date: "`r Sys.setlocale('LC_TIME','en_GB.utf8');format(Sys.Date(),'%d %B, %Y')`"
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/apa-cv.csl"
headcolor: 6767C7
docname: Academic Curriculum Vitae
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe |>
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) |>
  invisible()
```

# About me

```{r experiencia, echo = FALSE}
t.experiencia <- floor(year(Sys.time())-year(as.Date('01/01/09',format='%d/%m/%y')) - 1.5)
```

\begin{minipage}[c]{0.85\linewidth}
Psychologist, MSc in Basic and Applied Neurosciences, and PhD in Neurosciences. I am a researcher in cognitive neuroscience applied to human sexual behavior. My research integrates cognitive neuroscience, evolutionary psychology, and public health to understand how the brain processes sexually relevant information and how these mechanisms shape sexual attraction, mate preferences, sexual response, and sexual behavior. Using experimental methods—particularly eye tracking—I investigate both normative and atypical sexual interests, with the goal of advancing basic science and informing evidence-based strategies for the prevention of child sexual abuse and exploitation.
I am an Associate Professor at the \href{https://www.uelbosque.edu.co/psicologia}{Faculty of Psychology} at \href{https://www.uelbosque.edu.co/}{Universidad El Bosque} and an active associate researcher within the \href{https://investigaciones.unbosque.edu.co/codec}{\textit{\textbf{CODEC}: Cognitive and Behavioural Sciences}} Research Group (classified \href{https://scienti.minciencias.gov.co/gruplac/jsp/visualiza/visualizagr.jsp?nro=00000000001446}{\textbf{A1}} by MinCiencias). I lead the \href{https://grupo-codec.netlify.app/sexcog/}{\textit{\textbf{SexCog}: Sexuality and Affectivity from a Neurocognitive Perspective}} research hotbed and have led and co-led internally and externally funded research projects using experimental approaches in cognitive neuroscience. I completed a postdoctoral fellowship at \href{https://www.cuc.edu.co/}{Universidad de la Costa}, funded by \href{https://minciencias.gov.co/}{MinCiencias}.
Over the past `r t.experiencia` years, I have combined research and university teaching, contributing to undergraduate and graduate education in the neurobiological and cognitive bases of human behavior while supervising undergraduate, master's, and doctoral research projects.
\end{minipage}

# Skills

\begin{cvskills}
  \cvskill
    {Programming}
    {\href{https://www.r-project.org/}{\textbf{R}} (Basic, data analysis and graph generation)}

  \cvskill
    {Quantitative Research}
    {Observational-correlational studies, Simple and Mixed general linear models}
  
  \cvskill
    {Recording techniques}
    {Eye tracking (mainly), other basic HRV, EEG}

  \cvskill
    {Software}
    {RStudio, Tobii Pro Lab, Qualtrics, Psychomorph, WebmorphR, Mendeley and Zotero}

  \cvskill
    {Languages}
    {English/Spanish (native)}
\end{cvskills}

# Research

\begin{cvskills}

  \cvskill
    {Research Areas}
    {\textbf{Cognitive neuroscience of human sexual behavior • Sexual attraction \& response • Evolutionary psychology of mate choice • Atypical sexual interests • Prevention of child sexual abuse \& online child sexual exploitation}}

  \cvskill
    {Primary Research Methods}
    {Eye tracking • Experimental cognitive neuroscience • Free-viewing \& forced-choice paradigms • Facial stimulus manipulation (Psychomorph) • Psychophysiological measures • Psychometric assessment • Quantitative data analysis}

\end{cvskills}

# Education

```{r education}
readxl::read_excel("../data/education_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Relevant further education

```{r edu_comp}
readxl::read_excel("../data/edu_comp_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Academic Experience

```{r teaching-experience}
readxl::read_excel("../data/teaching-experience_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Research Experience

```{r research-experience}
readxl::read_excel("../data/research-experience_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Professional Experience

```{r working-experience}
readxl::read_excel("../data/working-experience_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Grants

```{r grant}
readxl::read_excel("../data/grant_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Scholarships, Awards and Honors

```{r award}
readxl::read_excel("../data/award_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Publications

```{r scholar, echo = FALSE}
profile <- get_profile("XgNEpfgAAAAJ")
pubs <- get_publications("XgNEpfgAAAAJ")

h_index <- profile$h_index
g_index <- max(which(as.numeric(row.names(pubs))^2 < cumsum(pubs$cites)))
i10_index <- profile$i10_index
pubs_num <- dim(pubs)[1]
citSum <- profile$total_cites
meancit <- round(mean(pubs$cites), 2)
mediancit <- median(pubs$cites)
```

\begin{tcolorbox}[enhanced,
        on line, 
        boxsep=4pt, left=0pt,right=0pt,top=0pt,bottom=0pt,
        colframe=white,colback=violet,
        hyperurl={https://scholar.google.com/citations?user=XgNEpfgAAAAJ}]
  
\color{white}
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center} 
      \begin{huge} `r h_index` \end{huge}
     \begin{small} \textit{h}-index \end{small} 
    \end{center} 
  \end{minipage} 
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center} 
      \begin{huge} `r g_index` \end{huge}
      \begin{small} \textit{g}-index \end{small} 
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center} 
      \begin{huge} `r i10_index` \end{huge}
      \begin{small} i10-index \end{small} 
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center}  
      \begin{huge} `r pubs_num` \end{huge}
      \begin{small} Publications \end{small} 
    \end{center}
  \end{minipage} 
  
  \begin{center} \noindent\line(1,0){150} Citations \noindent\line(1,0){150} \end{center}
  
  \begin{minipage}[c]{0.325\linewidth}  
    \begin{center} 
      \begin{small} Total \end{small} 
      \begin{LARGE} `r citSum` \end{LARGE} 
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.325\linewidth}
    \begin{center} 
      \begin{small} Mean \end{small} 
      \begin{LARGE} `r meancit` \end{LARGE}
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.325\linewidth}
    \begin{center}  
      \begin{small} Median \end{small} 
      \begin{LARGE} `r mediancit` \end{LARGE}
   \end{center}
  \end{minipage} 
\end{tcolorbox}

## \textbf{Journal Articles}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/journal.txt")`

\endgroup

## \textbf{Articles under Review}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/working_paper.txt")`

\endgroup

# Conference Presentations, Posters and Workshops

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/poster_en.txt")`

\endgroup

# Organisation of Scientific Events

```{r event}
readxl::read_excel("../data/event_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Research Supervision

## \textbf{Postgraduate}

```{r supervision}
readxl::read_excel("../data/supervision_pos_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

## \textbf{Undergraduate}

```{r supervision-pre}
readxl::read_excel("../data/supervision_pre_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```
