---
graphics: yes
name: Milena
surname: Vásquez-Amézquita
position: "Associate Professor"
address: "Faculty of Psychology, Universidad El Bosque"
phone: (+57) 601-6489000 Ext. 1605
email: "mvasquezam@unbosque.edu.co"
www: grupo-codec.netlify.app/author/milena-vasquez-amezquita/
orcid: 0000-0001-7317-8430
googlescholar: XgNEpfgAAAAJ
researchgate: Milena-Vasquez-Amezquita
profilepic: "../images/MVA.jpg"
aboutme: |
  I am a researcher primarily interested in the neurocognitive bases of human affect and sexuality.
date: "`r Sys.setlocale('LC_TIME','en_GB.utf8');format(Sys.Date(),'%d %B, %Y')`"
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/apa-cv.csl"
headcolor: 6767C7
docname: Academic Curriculum Vitae
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe |>
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) |>
  invisible()
```

# About me

```{r experiencia, echo = FALSE}
t.experiencia <- floor(year(Sys.time())-year(as.Date('01/01/09',format='%d/%m/%y')) - 1.5)
```

\begin{minipage}[c]{0.85\linewidth}
Psychologist, Master in Basic and Applied Neurosciences and PhD in Neurosciences. Active associate researcher within the group \href{https://investigaciones.unbosque.edu.co/codec}{\textit{\textbf{CODEC}: Cognitive and Behavioural Sciences}} (classification \href{https://scienti.minciencias.gov.co/gruplac/jsp/visualiza/visualizagr.jsp?nro=00000000001446}{\textbf{A1}} in MinCiencias). Associate Professor at the \href{https://grupo-codec.netlify.app/labpsiexp/}{\textbf{Laboratory of Experimental Psychology}} of the \href{https://www.uelbosque.edu.co/psicologia}{Faculty of Psychology} at \href{https://www.uelbosque.edu.co/}{Universidad El Bosque}. Postdoctoral stay at \href{https://www.cuc.edu.co/}{Universidad de la Costa} with funding from \href{https://minciencias.gov.co/}{MinCiencias}. I have been director and co-director of successful research projects from an experimental methodology in cognitive-affective neuroscience with internal and external funding, and I currently directing the research hotbed \href{https://grupo-codec.netlify.app/sexcog/}{\textit{\textbf{SexCog}: sexuality and affectivity from a neurocognitive perspective}}. I have `r t.experiencia` years of professional and university teaching experience, applied to the development and implementation of undergraduate and postgraduate higher education programmes related to the neurobiological and cognitive bases of human behaviour, and I have supervised undergraduate, masters and doctoral degree projects.
\end{minipage} \begin{minipage}[c]{0.15\linewidth}
\begin{flushright} 
\hfill \href{https://grupo-codec.netlify.app/sexcog/}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_SEXCOG.png}} \newline \href{https://investigaciones.unbosque.edu.co/codec}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_CODEC.png}}
\end{flushright}
\end{minipage}

# Skills

\begin{cvskills}
  \cvskill
    {Programming}
    {\href{https://www.r-project.org/}{\textbf{R}} (Basic, data analysis and graph generation)}

  \cvskill
    {Quantitative Research}
    {Observational-correlational studies, Simple and Mixed general linear models}
  
  \cvskill
    {Recording techniques}
    {Eye tracking (mainly), other basic HRV, EEG}

  \cvskill
    {Software}
    {RStudio, Tobii Pro Lab, Qualtrics, Psychomorph, WebmorphR, Mendeley and Zotero}

  \cvskill
    {Languages}
    {English/Spanish (native)}
\end{cvskills}

# Research

\begin{cvskills}
  \cvskill
    {Research Areas}
    {\textbf{Human sexual response • Typical and atypical sexual preferences • Pedohebephilia • Harmful sexual \newline behaviors • Mate choice • Attentional biases}}

  \cvskill
    {Primary Research Methods}
    {Experimental designs • Free viewing \& forced stimulus choice paradigms • Psychometric scales • Subjective \newline assessment of visual stimuli}
\end{cvskills}

# Education

```{r education}
readxl::read_excel("../data/education_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Relevant further education

```{r edu_comp}
readxl::read_excel("../data/edu_comp_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Academic Experience

```{r teaching-experience}
readxl::read_excel("../data/teaching-experience_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Research Experience

```{r research-experience}
readxl::read_excel("../data/research-experience_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Professional Experience

```{r working-experience}
readxl::read_excel("../data/working-experience_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Grants

```{r grant}
readxl::read_excel("../data/grant_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Scholarships, Awards and Honors

```{r award}
readxl::read_excel("../data/award_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Publications

```{r scholar, echo = FALSE}
profile <- get_profile("XgNEpfgAAAAJ")
pubs <- get_publications("XgNEpfgAAAAJ")

h_index <- profile$h_index
g_index <- max(which(as.numeric(row.names(pubs))^2 < cumsum(pubs$cites)))
i10_index <- profile$i10_index
pubs_num <- dim(pubs)[1]
citSum <- profile$total_cites
meancit <- round(mean(pubs$cites), 2)
mediancit <- median(pubs$cites)
```

\begin{tcolorbox}[enhanced,
        on line, 
        boxsep=4pt, left=0pt,right=0pt,top=0pt,bottom=0pt,
        colframe=white,colback=violet,
        hyperurl={https://scholar.google.com/citations?user=XgNEpfgAAAAJ}]
  
\color{white}
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center} 
      \begin{huge} `r h_index` \end{huge}
     \begin{small} \textit{h}-index \end{small} 
    \end{center} 
  \end{minipage} 
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center} 
      \begin{huge} `r g_index` \end{huge}
      \begin{small} \textit{g}-index \end{small} 
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center} 
      \begin{huge} `r i10_index` \end{huge}
      \begin{small} i10-index \end{small} 
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.245\linewidth}
    \begin{center}  
      \begin{huge} `r pubs_num` \end{huge}
      \begin{small} Publications \end{small} 
    \end{center}
  \end{minipage} 
  
  \begin{center} \noindent\line(1,0){150} Citations \noindent\line(1,0){150} \end{center}
  
  \begin{minipage}[c]{0.325\linewidth}  
    \begin{center} 
      \begin{small} Total \end{small} 
      \begin{LARGE} `r citSum` \end{LARGE} 
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.325\linewidth}
    \begin{center} 
      \begin{small} Mean \end{small} 
      \begin{LARGE} `r meancit` \end{LARGE}
    \end{center}
  \end{minipage} 
  \begin{minipage}[c]{0.325\linewidth}
    \begin{center}  
      \begin{small} Median \end{small} 
      \begin{LARGE} `r mediancit` \end{LARGE}
   \end{center}
  \end{minipage} 
\end{tcolorbox}

## \textbf{Journal Articles}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/journal.txt")`

\endgroup

## \textbf{Articles under Review}

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/working_paper.txt")`

\endgroup

# Conference Presentations, Posters and Workshops

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/poster_en.txt")`

\endgroup

# Organisation of Scientific Events

```{r event}
readxl::read_excel("../data/event_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Research Supervision

## \textbf{Postgraduate}

```{r supervision}
readxl::read_excel("../data/supervision_pos_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

## \textbf{Undergraduate}

```{r supervision-pre}
readxl::read_excel("../data/supervision_pre_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

