---
graphics: yes
name: Milena
surname: Vásquez-Amézquita
position: "Associate Professor"
address: "Faculty of Psychology, Universidad El Bosque"
phone: (+57) 601-6489000 Ext. 1605
email: "mvasquezam@unbosque.edu.co"
www: grupo-codec.netlify.app/author/milena-vasquez-amezquita/
orcid: 0000-0001-7317-8430
googlescholar: X58RxbIAAAAJ
researchgate: Milena-Vasquez-Amezquita
profilepic: "../images/MVA.jpg"
aboutme: |
  I am a researcher primarily interested in the neurocognitive bases of human affect and sexuality.
date: "`r Sys.setlocale('LC_TIME','en_GB.utf8');format(Sys.Date(),'%d %B, %Y')`"
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/apa-cv.csl"
headcolor: 6767C7
docname: Abbreviated Curriculum Vitae
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe |>
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) |>
  invisible()
```

# About me

```{r experiencia, echo = FALSE}
t.experiencia <- floor(year(Sys.time())-year(as.Date('01/01/09',format='%d/%m/%y')) - 1.5)
```

\begin{minipage}[c]{0.85\linewidth}
Psychologist, MSc in Basic and Applied Neurosciences, and PhD in Neurosciences. I am a researcher in cognitive neuroscience applied to human sexual behavior. My research integrates cognitive neuroscience, evolutionary psychology, and public health to understand how the brain processes sexually relevant information and how these mechanisms shape sexual attraction, mate preferences, sexual response, and sexual behavior. Using experimental methods—particularly eye tracking—I investigate both normative and atypical sexual interests, with the goal of advancing basic science and informing evidence-based strategies for the prevention of child sexual abuse and exploitation.

I am an Associate Professor at the \href{https://www.uelbosque.edu.co/psicologia}{Faculty of Psychology} at \href{https://www.uelbosque.edu.co/}{Universidad El Bosque} and an active associate researcher within the \href{https://investigaciones.unbosque.edu.co/codec}{\textit{\textbf{CODEC}: Cognitive and Behavioural Sciences}} Research Group (classified \href{https://scienti.minciencias.gov.co/gruplac/jsp/visualiza/visualizagr.jsp?nro=00000000001446}{\textbf{A1}} by MinCiencias). I lead the \href{https://grupo-codec.netlify.app/sexcog/}{\textit{\textbf{SexCog}: Sexuality and Affectivity from a Neurocognitive Perspective}} research hotbed and have led and co-led internally and externally funded research projects using experimental approaches in cognitive neuroscience. I completed a postdoctoral fellowship at \href{https://www.cuc.edu.co/}{Universidad de la Costa}, funded by \href{https://minciencias.gov.co/}{MinCiencias}.

Over the past `r t.experiencia` years, I have combined research and university teaching, contributing to undergraduate and graduate education in the neurobiological and cognitive bases of human behavior while supervising undergraduate, master's, and doctoral research projects.
\end{minipage} \begin{minipage}[c]{0.15\linewidth}
\begin{flushright} 
\hfill \href{https://grupo-codec.netlify.app/sexcog/}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_SEXCOG.png}} \newline \href{https://investigaciones.unbosque.edu.co/codec}{\includegraphics[width=2.3cm, height=2.3cm]{Logo_CODEC.png}}
\end{flushright}
\end{minipage}

# Skills

\begin{cvskills}
  \cvskill
    {Programming}
    {\href{https://www.r-project.org/}{\textbf{R}} (Basic, data analysis and graph generation)}

  \cvskill
    {Quantitative Research}
    {Observational-correlational studies, Simple and Mixed general linear models}
  
  \cvskill
    {Recording techniques}
    {Eye tracking (mainly), other basic HRV, EEG}

  \cvskill
    {Software}
    {RStudio, Tobii Pro Lab, Qualtrics, Psychomorph, WebmorphR, Mendeley and Zotero}

  \cvskill
    {Languages}
    {English/Spanish (native)}
\end{cvskills}

# Education

```{r education}
readxl::read_excel("../data/education_eng_S.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Research Experience

```{r research-experience}
readxl::read_excel("../data/research-experience_eng_S.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Professional Experience

For a full list, and a description of responsibilities, please check my [academic CV](https://jdleongomez.github.io/Mile_CV/CV_eng/MVA_CV_en.pdf).

```{r working-experience}
readxl::read_excel("../data/working-experience_eng_S.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Grants

```{r grant}
readxl::read_excel("../data/grant_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Scholarships, Awards and Honors

```{r award}
readxl::read_excel("../data/award_en.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```

# Selected Publications

```{r scholar, echo = FALSE}
scholar_id <- "X58RxbIAAAAJ"
cache_file <- "../scholar_cache.rds"

if (isTRUE(getOption("mva_scholar_cache_only"))) {
  scholar_data <- if (file.exists(cache_file)) readRDS(cache_file) else NULL
} else {
  scholar_data <- tryCatch({
    data <- list(
      profile = get_profile(scholar_id),
      pubs    = get_publications(scholar_id)
    )
    saveRDS(data, cache_file)
    data
  }, error = function(e) {
    message("Scholar fetch failed: ", conditionMessage(e))
    if (file.exists(cache_file)) {
      message("Loading cached Scholar data.")
      readRDS(cache_file)
    } else {
      message("No cache available. Citation metrics will show NA.")
      NULL
    }
  })
}

if (!is.null(scholar_data) && is.list(scholar_data$profile)) {
  profile   <- scholar_data$profile
  h_index   <- profile$h_index
  i10_index <- profile$i10_index
  citSum    <- profile$total_cites
  if (!is.null(scholar_data$pubs) && nrow(scholar_data$pubs) > 0) {
    pubs     <- scholar_data$pubs
    g_index  <- max(which(as.numeric(row.names(pubs))^2 < cumsum(pubs$cites)))
    pubs_num <- dim(pubs)[1]
  } else {
    g_index  <- if (!is.null(profile$g_index))  profile$g_index  else NA
    pubs_num <- if (!is.null(profile$pubs_num)) profile$pubs_num else NA
  }
} else {
  h_index <- g_index <- i10_index <- pubs_num <- citSum <- NA
}
```

\begin{tcolorbox}[enhanced,
        on line, 
        boxsep=4pt, left=0pt,right=0pt,top=0pt,bottom=0pt,
        colframe=white,colback=violet,
        hyperurl={https://scholar.google.com/citations?user=X58RxbIAAAAJ}]
  
\color{white}
\begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r h_index` \end{huge}
  \begin{small} \textit{h}-index \end{small} \end{center} 
\end{minipage} \begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r g_index` \end{huge}
  \begin{small} \textit{g}-index \end{small} \end{center}
\end{minipage} \begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r i10_index` \end{huge}
  \begin{small} i10-index \end{small} \end{center}
\end{minipage} \begin{minipage}[c]{0.195\linewidth}
  \begin{center} \begin{huge} `r pubs_num` \end{huge}
  \begin{small} Publications \end{small} \end{center}
\end{minipage} \begin{minipage}[c]{0.195\linewidth}  
  \begin{center} \begin{huge} `r citSum` \end{huge} 
  \begin{small} Citations \end{small} \end{center}
\end{minipage}
\end{tcolorbox}

For a full list, please check the publications section on my [academic CV](https://jdleongomez.github.io/Mile_CV/CV_eng/MVA_CV_en.pdf).

\begingroup
\footnotesize
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("../bib/featured.txt")`

\endgroup

# Postgraduate Supervision

For a full list, including undergraduate supervision, please check my [academic CV](https://jdleongomez.github.io/Mile_CV/CV_eng/MVA_CV_en.pdf).

```{r supervision}
readxl::read_excel("../data/supervision_eng_S.xlsx") |>
  tidyr::fill(-why) |>
  vitae::detailed_entries(what, when, with, where, why,
                          .protect = FALSE)
```
